Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2013-01-05 chi2013-webbox.tex
mor etext

\section{Introduction}
In recent years, an unprecedented quantity and variety of information has been made available as structured data on the Web.  The explosion of structured data APIs and downloadable data sets has arrived from many different sectors, including retail, banking, social networking, opinion and recommendation sites, mobile and desktop apps, as well as from new kinds sensors and devices such as wearable activity and bio-sensors. In addition to commercial apps and services, governments have embraced open data as a way of providing transparency and accountability to their citizens, causing a huge push to release data at scales ranging from the smallest local councils to entire national departments.  A common goal for the release of such data has been to provide end-user citizens an ability to make more informed decisions pertaining to their health, wealth, and well-being \cite{Shadbolt:2006:SWR:1155313.1155373}.  Thus far, however, this data has been predominately used by app developers, journalists and other ``data specialists'' to perform ``one-off'' data analyses and investigations, but has remained inaccessible to citizens because of a lack of suitable tools with which these data sets can be easily manipulated and explored.  For example, the most familiar kinds of personal information management (PIM) tools only provide facilities for managing small, fixed sets of data types (such as digital calendaring tools and to-do list managers) or provide little or no support for structured data at all, such as text editors and sketching/drawing tools \cite{infoscraps}.

>>>>

\section{Introduction}
In recent years, an unprecedented quantity and variety of information has been made available as structured data on the Web.  The explosion of structured data APIs and downloadable data sets has arrived from many different sectors, including retail, banking, social networking, opinion and recommendation sites, mobile and desktop apps, as well as from new kinds sensors and devices such as wearable activity and bio-sensors. Beyond commercial apps and services, governments have embraced releasing data as a way of providing transparency and accountability to their citizens, causing a huge push to release ``open data'' to the public, at scales ranging from the smallest local councils to entire national departments.

A common goal for the release of such data has been to provide end-user citizens an ability to make more informed decisions pertaining to their health, wealth, and well-being \cite{Shadbolt:2006:SWR:1155313.1155373}.  Thus far, however, this data has been predominately been consumed by app developers, journalists and other ``data specialists'' in one-off data analyses, apps and investigations, remaining still far from influencing the activities of ordinary end-user citizens. A core reason for this, we posit, is a lack of suitable tools for accessing and interrogating these heterogeneous data sets, and a means by which these disparate information sources can be effectively brought together and cross-referenced.  For example, most personal information management (PIM) tools only provide facilities for managing small, pre-fixed sets of data types (such as digital calendaring tools and to-do list managers) or provide little or no support for structured data at all, such as text editors and sketching/drawing tools \cite{infoscraps}.
